temp

### 2025-07-17 Writing/manuscript_CF_continuous.qmd
comments added to the manuscript

@@

# Materials and Method

@@

@@

@@

@@

$$
Y=f(X, N)+v
$$
Once $f(X, N)$ is estimated (denote it as $\hat{f}(X, N)$ ), then the conditional treatment effect of moving from one rate ( $N_0$ ) to another ( $N_1$ ) can be obtained by $\hat{f}\left(X, N_1\right)-\hat{f}\left(X, N_0\right)$. The associated change in profit is $P_{\text {corn }} \hat{f}\left(X, N_1\right)-P_{\text {corn }} \hat{f}\left(X, N_0\right)-P_N\left(N_1-N_0\right)$. Similar to the CF approach, a grid search is used to identify numerically the optimal nitrogen rate.

@@

@@

@@

$$
R M S E_{E O N R}=\sqrt{\frac{1}{n} \sum_{i=1}^n\left(\widehat{E O N R}_i-E O N R_i\right)^2}

$$
To assess the predictive accuracy and economic relevance of these modeling approaches, we design a set of simulation experiments that reflect realistic agronomic conditions. These simulations serve as a controlled environment for evaluating model performance in estimating yield response functions and recommending optimal nitrogen rates.

>>>>

---
title: "temp"
format:
  html: default
execute:
  echo: false
---

```{r}
#| include: false
library(data.table) 
library(dplyr) 
library(flextable) 
library(officer) 
```

@@

# Method

We run Monte Carlo simulation to test the performance of ...

@@

<span style = "color: blue;"> Explain the types of estimation you do first in general. You have double-orthogonalized, single-orthogonalized, and non-orthogonalized. The difference among the models we try are in how we do the orthogonalization and final stage estimation. The table below shows all the cases you consider. </span>

<span style = "color: blue;"> Use tex and align environment for equations like below instead of using $$. </span>

```{=tex}
\begin{align*}
Y = f(X)
\end{align*}
```

```{r}
#| include: false
f_est <-
  data.table(
    "Approach Label" = c("DO-NN", "SO-RFF", "SO-NN", "DO-CF","NO-NN", "NO-RF"),
    "Approach Type" = c("Double-orthogonalized", "Single-orthogonalized", "Single-orthogonalized", "Double-orthogonalized", "Non-orthogonalized", "Non-orthogonalized"),
    "Y-orthogonalization" = c("Randome Forest", "Randome Forest", "Randome Forest", "Randome Forest", "NA", "NA"),
    "T-orthogonalization" = c("Randome Forest", "NA", "NA", "Randome Forest", "NA", "NA"),
    "Final stage" = c("Neural Network", "Random Forest", "Neural Network", "Causal Forest", "Neural Network", "Random Forest")
  ) %>%
  flextable() %>%
  fontsize(size = 16, part = "all") %>%
  autofit()

flextable::save_as_image(f_est, here::here("writing/f_est.png"), res = 300)
```

```{r}
#| echo: false
#| fig-width: 4
#| out-width: 4in
knitr::include_graphics(here::here("writing/f_est.png"))
```

@@

<span style = "color: red;"> Right now, you are explaining how EONR is calculated by method. But, all the estimation cases follow the same procedure. For all cases, you have $\hat{y} = \hat{f}(N:X)$. So, you can just this function in explaining how to get EONR for all the cases. You are repeating the same equations of profit three times. You should recognized that problem. Think carefully how to structure the section. Don't just write. </span>

### Non-orthogonalized ANN (NO-NN) and RF (NO-RF)

<span style = "color: blue;"> I am adding NO-RF as one of the method to consider. Write code for this and get the results. It should be easy. </span>

Neither of Y or X is orthogonalized

$$
Y=f(X, N)+v
$$

<span style = "color: blue;"> As I said, remove the sentences below. </span>

Once $f(X, N)$ is estimated (denote it as $\hat{f}(X, N)$ ), then the conditional treatment effect of moving from one rate ( $N_0$ ) to another ( $N_1$ ) can be obtained by $\hat{f}\left(X, N_1\right)-\hat{f}\left(X, N_0\right)$. The associated change in profit is $P_{\text {corn }} \hat{f}\left(X, N_1\right)-P_{\text {corn }} \hat{f}\left(X, N_0\right)-P_N\left(N_1-N_0\right)$. Similar to the CF approach, a grid search is used to identify numerically the optimal nitrogen rate.

### CF-continuous

<span style = "color: blue;"> This is an inaccurate and insufficient explanations. Add what I wrote for CF in the manuscript I shared. </span>

@@

<span style = "color: blue;"> This is a description for binary treatment case. After running CF-continuous, you are getting $\hat{y} = \hat{f}(N:X)$</span>

@@

### Double-orthogonalized ANN (DO-ANN) and RF (DO-RFF)

@@

### Single-orthogonalized NN (SO-NN) and (SO-RF)

<span style = "color: blue;"> Once you explain how SO works. The difference between SO-NN and SO-RF is just the final stage estimation. Write that way to reduce unnecessary writing</span>

@@

## Estimation of site-specific EONR

@@

```{=tex}
\begin{align*}
RMSE_{EONR}=\sqrt{\frac{1}{n} \sum_{i=1}^n\left(\widehat{EONR}_i-EONR_i\right)^2}
\end{align*}
```

To assess the predictive accuracy and economic relevance of these modeling approaches, we design a set of simulation experiments that reflect realistic agronomic conditions. These simulations serve as a controlled environment for evaluating model performance in estimating yield response functions and recommending optimal nitrogen rates.
